Tor's Usability for Censorship Circumvention

### 2015-10-14 paper/circumvention-experiment.tex
added bit about methodology

@@

\noindent {\bfseries Experiment Logistics} 
The IRB protocol to run this user study has been approved (2014-12-6995). 
We plan to recruit 100-200 users for the purpose of this study,
making it the largest user study of Tor to date.  This study will be conducted at the
Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley, which consists of 36 laptops,
separated by cubicle walls. We will use individual host firewalls to simulate
censorship environments and will record computer screens to capture 
user activity. The total length of the experiment, including briefing, completing the censorship 
circumvention tasks, exit survey, and debriefing, will be about an hour.
Participants will be compensated \$30 for their time, which covers
minimum wage for an hour and any transportation costs to the lab.  \\

>>>>

\section{Methodology}

We are going to aim for 5 users per censorship environment, improvement, 
and alternate interface. We are going to pre-screen our participants so that 
we have a good mix of gender, age, technical background, and familiarity 
with Tor.

Some references to keep in mind when explaining: 
\href{why 5 users}{http://www.nngroup.com/articles/how-many-test-users/}
\href{screening}{http://www.userfocus.co.uk/articles/screeners.html}
\href{summative and usability mixed model}{http://www.usabilitybok.org/summative-usability-testing}

@@

\noindent {\bfseries Experiment Logistics} 
The IRB protocol to run this user study has been approved (2014-12-6995). 
We plan to recruit 35-50 users for the purpose of this study,
making it the largest user study of Tor to date.  This study will be conducted at the
Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley, which consists of 36 laptops,
separated by cubicle walls. We will use individual host firewalls to simulate
censorship environments and will record computer screens to capture 
user activity. The total length of the experiment, including briefing, completing the censorship 
circumvention tasks, exit survey, and debriefing, will be about an hour.
Participants will be compensated \$30 for their time, which covers
minimum wage for an hour and any transportation costs to the lab.  \\
